Asymmetric relationships and their effects on coexistence: Supporting information

### 2023-07-31 paper/SupMat.Rnw
editted new additions explaining intuition of ATA effects, now done, moving on

Just as for storage effects [see \cite{Chesson_1994} and Box 2 of \cite{StumpVasseur2023}], 
temporal niche differentiation is necessary in order for ATA
effects to materialize; we here explain why, in detail. ``Lack of temporal niche differentiation'' can be interpreted
to mean that species respond in identical ways to environmental fluctuations. 
In a two-species model such as those we consider, this should mean a monotonically
increasing relationship between $E_i$ and $C_{i \bs i}$. The former is the environment
as perceived by species $i$. The latter is competition that a scarce invader $i$ experiences
in a monoculture of $j$, and that competition comes only from $j$ (because $i$ itself
is scarce), so should correspond to the environmental response of $j$. If 
$E_i$ and $C_{i \bs i}$ are monotonically related, then $(E_i,C_{i \bs i})$
and $(E_i^\nat,C_{i \bs i}^\nat)$ are distributed in the same way, so 
$\E[r_i(E_i,c_{i \bs i})]-\E[r_i(E_i^\nat,c_{i \bs i}^\nat)]=0$.
Therefore, 
\begin{align}
\Delta_i^{[EC]} &= (\olr_{i \bs i}-\olr_{j \bs i})-(\olr_{i \bs i}^\nat - \olr_{j \bs i}^\nat) \\
&= \olr_{i \bs i}-(\olr_{i \bs i}^\nat - \olr_{j \bs i}^\nat) \\
&= \E[r_i(E_i,C_{i \bs i})]-\E[r_i(E_i^\nat,C_{i \bs i}^\nat)]+\E[r_j(E_j^\nat,C_{j \bs i}^\nat)] \label{eq:expri}\\
&= \E[r_j(E_j^\nat,C_{j \bs i}^\nat)].
\end{align}
But we already know $\E[r_j(E_j^\nat,C_{j \bs i}^\nat)]=0$
because there is no niche differentiation between $j$ and itself, so 
$E_j$ and $C_{j \bs i}$ should be monotonically related. So 
$\E[r_j(E_j^\nat,C_{j \bs i}^\nat)] = \E[r_j(E_j,C_{j \bs i})]=0$, giving
$\Delta_i^{[EC]}=0$. So temporal
niche differentiation, interpreted as Spearman correlation between 
$E$ and $C$ less than $1$, is necessary for ATA effects on coexistence to 
materialize.

@@

If temporal niche differentiation occurs but is partial, 
then $E_i$ and $C_{i \bs i}$ will be positively but imperfectly correlated with
each other, corresponding to similar but non-identical responses of species to
environmental fluctuation (SI section \ref{SIsect:temporal_niche_diff}). 
But how do ATA effects then happen? We here extend the intuition
introduced in the Discussion and provide examples.

First, we illustrate using the beta fecundities lottery model that
the potential for storage to occur when 
$E$ and $C$ are both higher than average, versus the potential  
when $E$ and $C$ are
both lower than average, are not necessarily equivalent.
Storage can occur if population
increases during good years outweigh decreases during bad years. For instance,
if $r_i(E_i,C_{i \bs i})$ is very large when the balance of $E_i$ and 
$C_{i \bs i}$ is favorable, but only moderately small when this balance is
unfavorable, the expected value $\E[r_i(E_i,C_{i \bs i})]$ in (\ref{eq:expri})
will be positive. But the potential for such storage of population growth
may differ between when $E_i$ and $C_{i \bs i}$ are both high compared
to when they are both low. 
For instance, for the beta fecundities lottery model, $E_i/C_{i \bs i}$, a quantity
which features prominently in $r_i(E_i,C_{i \bs i})=\log(1-\delta+E_i/C_{i \bs i})$,
takes values bounded above by $\frac{2\eta_i \delta}{\eta_j}$ 
and bounded below by $\frac{\eta_i \delta}{2 \eta_j}$ when $E_i$ and $C_{i \bs i}$
are both in the upper halves of their assumed beta distributions (recall that 
these quantities were assumed to be distributed, respectively, as $\eta_1 \beta$
and $\eta_2 \beta/\delta$ for $\beta$ a beta-distributed random variable with parameters 
$0.5$ and $0.5$). These bounds are separated only by a factor of four. 
On the other hand, when $E_i$ and $C_{i \bs i}$ are both in the lower halves 
of their distributions, $E_i/C_{i \bs i}$ can take any positive value because
then either $E_i$ or $C_{i \bs i}$ can take values arbitrarily close to $0$. 
Because values of $E_i/C_{i \bs i}$ have the potential to be much larger when 
$E_i$ and $C_{i \bs i}$ are both in the lower halves of their distributions
than when these quantities are both in their upper halves, and because
the growth rate, $\log(1-\delta+E_i/C_{i \bs i})$, buffers low values of 
$E_i/C_{i \bs i}$ (the infemum of the growth rate is $\log(1-\delta)$, whereas the supremum is
infinite), the storage effects contributed by the left tails of 
$E_i$ and $C_{i \bs i}$ have the potential to be much greater than those contributed
by the right tails. Essentially, annual growth-when-rare rates for species $i$
that occur when $E_i$ and $C_{i \bs i}$ are both in the upper halves of their
distributions can never exceed $\log(1-\delta+\frac{2\eta_i \delta}{\eta_j})$,
whereas rates ocurring when $E_i$ and $C_{i \bs i}$ are both in the lower
halves of their distributions can be arbitrarily large. 
Apparently, the years with the most potential to 
contribute to storage
effects for the beta-fecundities lottery model are those for which the environment
is actually poorer than average, because, for those years, competition can be very low,
so that the ratio $E_i/C_{i \bs i}$ is large. Years for which the
environment is exceptionally good actually cannot contribute much to storage effects for 
this model, because for those years, $E_i/C_{i \bs i}$ cannot be very large.
It is the \emph{imbalance} between $E$ and $C$ that allows for storage effects,
not solely the quality of environment. 
Counterintuitively, that imbalance can be greater for this model when the environment is 
sub-optimal.

Fig. \ref{fig:beta_fecundidities_explanatory} provides quantitative backing to
the ideas of the prior paragraph, so we orient the reader 
to the figure before using it below to further explain
ATAs. The growth function $\ln(1-\delta+E/C)$ that pertains to the lottery model
is plotted with colors and contours on Fig. \ref{fig:beta_fecundidities_explanatory}A-C.
Samples were taken from the distribution $(E_i,C_{i \bs i})$ for the beta 
fecundities lottery model for left- and right-tailed 
associations between $E_i$ and $C_{i \bs i}$, and are plotted as
points on Fig. \ref{fig:beta_fecundidities_explanatory}A and C, respectively. 
Samples were also taken from the distribution $(E_i^\nat,C_{i \bs i}^\nat)$
(which is the same regardless of whether the original $(E_i,C_{i \bs i})$
distribution showed left- or right-tail association) and are plotted on 
Fig. \ref{fig:beta_fecundidities_explanatory}B. 
The dashed lines labelled $L_2$ on A-C separate the upper-right $50\%$
of each distribution from the lower-left $50\%$, and those portions are labelled. 
The quantity $\E \left[ \ln \left( 1-\delta+\frac{E_i}{C_{i \bs i}} \right) \right]$ can be
well approximated, for left- and right-tail association cases, by averaging values of the
function depicted with color and contours over the points on panels A and C, 
respectively. The quantity
$\E \left[ \ln \left( 1-\delta+\frac{E_i^{||}}{C_{i \bs i}^{||}} \right) \right]$
can be well approximated by averaging function 
values over the points on B. So ATA effects for the model with left-tail association
between $E_i$ and $C_{i \bs i}$ (respectively, right-tail association) are given by 
computing the average function value over points on panel A (respectively, C)
and then subtracting the average function value over points on panel B.
Contributions to the storage effect of points in the left portions of 
the $E,C$ distribution (the region labeled ``left'' on panels A and C)
can be accurately estimated by averaging function values across
points in that region; likewise storage contributions of points in the 
``right'' region can be estimated by averaging function values over 
points in that region.

The details of the averaging processes described above are pictured in 
Fig. \ref{fig:beta_fecundidities_explanatory}, panels D-F. 
Signed distances of points on Fig. \ref{fig:beta_fecundidities_explanatory} 
A-C from the lines $L_1$ correspond to 
the quantities $\log_{10}(E_1/C_{1 \bs 1})$ on A, C and to 
$\log_{10}(E_1^\nat/C_{1 \bs 1}^\nat)$ on B. The distributions of these 
quantities across points in the ``left'' region are pictured 
in the lower horizontal-axis histograms on panels D-F, respectively;
and distributions for points in the ``right'' region are 
pictured in the upper horizontal-axis histograms. 
``Right'' histograms on the horizontal axis of D,F are always highly 
concentrated, corresponding to the fact that, for the beta fecundities
lottery model, $E_i/C_{i \bs i}$ cannot vary much when $E_i$ and 
$C_{i \bs i}$ are in the upper portions of their distributions. 
Likewise, the ``right'' histogram on E is highly concentrated because
$E_i^\nat/C_{i \bs i}^\nat$ cannot vary much when $E_i^\nat$ and 
$C_{i \bs i}^\nat$ are in the upper portions of their distributions.
In contrast, ``left'' histograms on the horizontal axis of D-F
can be highly variable, though only when $E_i$ and $C_{i \bs i}$
(or $E_i^\nat$ and $C_{i \bs i}^\nat$) are not tightly 
correlated in the left portions of their distributions.
The function pictured with a black line on panels D-F is simply the function
$z \rightarrow \ln(1-\delta+10^z)$ that takes $z=\log_{10}(E_1,C_{1 \bs 1})$
to $\ln(1-\delta+E_1/C_{1 \bs 1})$, representing growth rate for the model.
Storage effects are manifest by this function, because it is flat on the left and 
upward sloping on the right, so highly variable horizontal-axis inputs to the function
can translate into higher average vertical-axis values than can concentrated
horizontal-axis inputs of the same mean; e.g., the histograms labeled ``left'' on
E,F. Red dots indicate the mean values of
each histogram. The average vertical-axis values of the two red dots on each panel
equal the GWR of species $i$ for the model (value displayed numerically).

We now relate Fig. \ref{fig:beta_fecundidities_explanatory} back to ATAs. Coexistence is possible for 
right-tail association (panel F, positive GWR) but impossible for left-tail association (panel D,
negative GWR). Coexistence is possible for the right-tail case essentially
because the points in the ``left'' region in C produce highly variable
annual growth rates, which lead to storage effects; the same effect does 
not occur for the left-tail case because 
points in the ``left'' region on panel A are concentrated on line $L_1$ because of the
strong left-tail association of $E_i$ and $C_{i \bs i}$ on that panel. 
Association, or lack thereof, in right tails makes little difference 
to mean growth rates because $E_i/C_{i \bs i}$ cannot vary much. Overall, ATA effects 
are positive for the right-tail case because strong association between 
$E_i$ and $C_{i \bs i}$ is concentrated in the right tails, where there 
is little potential for storage effects anyway; and so disassociation between
$E_i$ and $C_{i \bs i}$ occurs in the left tails, where there is much potential for
storage effects. For the actual quantification of ATA effects,
a comparison is made to the case of symmetric association 
(panels B, E), as a benchmark. What is assessed by ATA
effects is the degree to which patterns of disassociation between 
$E$ and $C$ align with the portions of $E,C$ distribution for which the potential
for storage effects is high. Larger ATA effects indicate better alignment.

Fig. \ref{fig:lognormal_fecundidities_explanatory} is similar to 
Fig. \ref{fig:beta_fecundidities_explanatory}, but is based on the log-normal 
fecundities lottery model instead of the beta fecundities lottery model. 
The figure illustrates that the potential for storage events is equivalent in
the upper and lower tails of the $EC$ distribution (labelled ``right'' and ``left'',
respectively, on panels A-C). That is why ATA effects are fairly modest for the 
log-normal fecundities lottery model for the both the left- and right-tail
associated cases.

@@

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/PostHocExplanatoryFig_betaFecund.jpg}
\caption[A detailed look at ATA effects for the beta fecundities lottery model]{A 
detailed look at ATA effects for the beta fecundities lottery model.
The figure gives a pictorial representation of the calculation of  
$\E \left[ \ln \left( 1-\delta+\frac{E_i}{C_{i \bs i}} \right) \right]$ (A, C, D, F) and 
$\E \left[ \ln \left( 1-\delta+\frac{E_i^{||}}{C_{i \bs i}^{||}} \right) \right]$ (B, E)
for the model, considering both left- (A, D) and right-tail (C, F) associations
between $E_i$ and $C_{i \bs i}$. ATA effects are the difference of these two values.
The figure also illustrates how ATAs reflect the degree of alignment between where 
in the $EC$ distributions associations are allocated and which parts of that distribution
have high potential for storage effects. See SI section \ref{SIsect:intuition_examples}
for details. We used model parameters $\eta_1 = 1$, $\eta_2 = 1.2$, and $\delta=0.6$
for this example.}\label{fig:beta_fecundidities_explanatory}
\end{figure}

>>>>

Just as for storage effects [see \cite{Chesson_1994} and Box 2 of \cite{StumpVasseur2023}], 
temporal niche differentiation is necessary in order for ATA
effects to materialize; we here explain why, in detail. ``Lack of temporal niche differentiation'' can be interpreted
to mean that species respond in identical ways to environmental fluctuations. 
In a two-species model such as those we consider, this should mean a monotonically
increasing relationship between $E_i$ and $C_{i \bs i}$. The former is the environment
as perceived by species $i$. The latter is competition that a scarce invader $i$ experiences
in a monoculture of $j$, and that competition comes only from $j$ (because $i$ itself
is scarce), so should correspond to the environmental response of $j$. Therefore, if the environmental
responses of the two species are the same, that should be reflected in a monotonic 
relationship between $E_i$ and $C_{i \bs i}$. Then, $(E_i,C_{i \bs i})$
and $(E_i^\nat,C_{i \bs i}^\nat)$ are distributed in the same way, so 
$\E[r_i(E_i,c_{i \bs i})]-\E[r_i(E_i^\nat,c_{i \bs i}^\nat)]=0$.
Therefore, 
\begin{align}
\Delta_i^{[EC]} &= (\olr_{i \bs i}-\olr_{j \bs i})-(\olr_{i \bs i}^\nat - \olr_{j \bs i}^\nat) \\
&= \olr_{i \bs i}-(\olr_{i \bs i}^\nat - \olr_{j \bs i}^\nat) \\
&= \E[r_i(E_i,C_{i \bs i})]-\E[r_i(E_i^\nat,C_{i \bs i}^\nat)]+\E[r_j(E_j^\nat,C_{j \bs i}^\nat)] \label{eq:expri}\\
&= \E[r_j(E_j^\nat,C_{j \bs i}^\nat)].
\end{align}
But we already know $\E[r_j(E_j^\nat,C_{j \bs i}^\nat)]=0$
because there is no niche differentiation between $j$ and itself, so 
$E_j$ and $C_{j \bs i}$ should be monotonically related. So 
$\E[r_j(E_j^\nat,C_{j \bs i}^\nat)] = \E[r_j(E_j,C_{j \bs i})]=0$, giving
$\Delta_i^{[EC]}=0$. So temporal
niche differentiation, interpreted as a relationship between 
$E$ and $C$ which is not simply monotonic, is necessary for ATA effects on coexistence to 
materialize. Such a non-monotonic relationship occurs if  
the Spearman correlation between 
$E$ and $C$ is less than $1$.

@@

If temporal niche differentiation occurs but is partial, 
so that $E_i$ and $C_{i \bs i}$ are positively but imperfectly correlated with
each other, corresponding to similar but non-identical responses of species to
environmental fluctuation (SI section \ref{SIsect:temporal_niche_diff}), 
how do ATA effects then happen? We here extend the intuition
introduced in the Discussion and provide examples.

First, we illustrate using the beta fecundities lottery model that
the potential for storage to occur when 
$E$ and $C$ are both higher than average, versus the potential  
when $E$ and $C$ are
both lower than average, are not necessarily equivalent.
Recall that storage of population growth can occur if population
increases during good years outweigh decreases during bad years. For instance,
if $r_i(E_i,C_{i \bs i})$ is very large when the balance of $E_i$ and 
$C_{i \bs i}$ is favorable, but only moderately small when this balance is
unfavorable, the expected value $\E[r_i(E_i,C_{i \bs i})]$ in (\ref{eq:expri})
will be positive. But the potential for such storage
may differ between when $E_i$ and $C_{i \bs i}$ are both high compared
to when they are both low. 
For instance, for the beta fecundities lottery model, $E_i/C_{i \bs i}$, a quantity
which features prominently in $r_i(E_i,C_{i \bs i})=\log(1-\delta+E_i/C_{i \bs i})$,
takes values bounded above by $\frac{2\eta_i \delta}{\eta_j}$ 
and bounded below by $\frac{\eta_i \delta}{2 \eta_j}$ when $E_i$ and $C_{i \bs i}$
are both in the upper halves of their assumed beta distributions (recall that 
these quantities were assumed to be distributed, respectively, as $\eta_1 \beta$
and $\eta_2 \beta/\delta$ for $\beta$ a beta-distributed random variable with parameters 
$0.5$ and $0.5$). These bounds are separated only by a factor of four. 
On the other hand, when $E_i$ and $C_{i \bs i}$ are both in the lower halves 
of their distributions, $E_i/C_{i \bs i}$ can take any positive value because
then either $E_i$ or $C_{i \bs i}$ can take values arbitrarily close to $0$. 
Because values of $E_i/C_{i \bs i}$ have the potential to be much larger when 
$E_i$ and $C_{i \bs i}$ are both in the lower halves of their distributions
than when these quantities are both in their upper halves, and because
the growth rate, $\log(1-\delta+E_i/C_{i \bs i})$, buffers low values of 
$E_i/C_{i \bs i}$ (the infemum of the growth rate is $\log(1-\delta)$, whereas the supremum is
infinite), the storage effects contributed by the left tails of 
$E_i$ and $C_{i \bs i}$ have the potential to be much greater than those contributed
by the right tails. Essentially, annual growth-when-rare rates for species $i$
that occur when $E_i$ and $C_{i \bs i}$ are both in the upper halves of their
distributions can never exceed $\log(1-\delta+\frac{2\eta_i \delta}{\eta_j})$,
whereas rates ocurring when $E_i$ and $C_{i \bs i}$ are both in the lower
halves of their distributions can be arbitrarily large. 
Apparently, the years with the most potential to 
contribute to storage
effects for species $i$ for the beta-fecundities lottery model are those for which the environment
is actually poorer than average for $i$, because, for those years, competition can be very low,
so that the ratio $E_i/C_{i \bs i}$ is large. Years for which the
environment is exceptionally good for $i$ actually cannot contribute much to storage effects for 
this model, because for those years, $E_i/C_{i \bs i}$ cannot be very large.
It is the \emph{imbalance} between $E$ and $C$ that allows for storage effects,
not solely the quality of environment. 
Counterintuitively, that imbalance can be greater for this model when the environment is 
sub-optimal for $i$.

Fig. \ref{fig:beta_fecundidities_explanatory} provides quantitative backing to
the ideas of the prior paragraph, so we orient the reader 
to the figure before using it below to further explain
ATA effects. The growth function $\ln(1-\delta+E/C)$ that pertains to the lottery model
is plotted with colors and contours on Fig. \ref{fig:beta_fecundidities_explanatory}A-C.
Samples were taken from the distribution $(E_i,C_{i \bs i})$ for the beta 
fecundities lottery model for left- and right-tailed 
associations between $E_i$ and $C_{i \bs i}$, and are plotted as
points on Fig. \ref{fig:beta_fecundidities_explanatory}A and C, respectively. 
Samples were also taken from the distribution $(E_i^\nat,C_{i \bs i}^\nat)$
(which is the same regardless of whether the original $(E_i,C_{i \bs i})$
distribution showed left- or right-tail association) and are plotted on 
Fig. \ref{fig:beta_fecundidities_explanatory}B. 
The dashed lines labelled $L_2$ on A-C separate the upper-right $50\%$
of each distribution from the lower-left $50\%$, and those portions are labelled. 
The quantity $\E \left[ \ln \left( 1-\delta+\frac{E_i}{C_{i \bs i}} \right) \right]$ can be
well approximated, for left- and right-tail association cases, by averaging values of the
function depicted with color and contours over the points on panels A and C, 
respectively (these average values are listed as ``growth'' on panels D and F
respectively). The quantity
$\E \left[ \ln \left( 1-\delta+\frac{E_i^{||}}{C_{i \bs i}^{||}} \right) \right]$
can be well approximated by averaging function 
values over the points on B (the average is listed as ``growth'' on E). 
So ATA effects for the model with left-tail association
between $E_i$ and $C_{i \bs i}$ (respectively, right-tail association) are given taking the
value labelled ``growth'' on panel D (respectively, F) and subtracting the value ``growth''
on E; a negative result for left-tail associations and a positive result for 
right-tail associations. 
Contributions to the storage effect of points in the left portions of 
the $E,C$ distribution (the region labeled ``left'' on panels A and C)
can be accurately estimated by averaging function values across
points in that region; likewise storage contributions of points in the 
``right'' region can be estimated by averaging function values over 
points in that region.

The details of the averaging processes described above are pictured in 
Fig. \ref{fig:beta_fecundidities_explanatory}, panels D-F. 
Signed distances of points on Fig. \ref{fig:beta_fecundidities_explanatory} 
A-C from the lines $L_1$ correspond to 
the quantities $\log_{10}(E_1/C_{1 \bs 1})$ on A, C and to 
$\log_{10}(E_1^\nat/C_{1 \bs 1}^\nat)$ on B. The distributions of these 
quantities across points in the ``left'' region are pictured 
in the lower horizontal-axis histograms on panels D-F, respectively;
and distributions for points in the ``right'' region are 
pictured in the upper horizontal-axis histograms. 
``Right'' histograms on the horizontal axis of D,F are always highly 
concentrated, corresponding to the fact that, for the beta fecundities
lottery model, $E_i/C_{i \bs i}$ cannot vary much when $E_i$ and 
$C_{i \bs i}$ are in the upper portions of their distributions. 
Likewise, the ``right'' histogram on E is highly concentrated because
$E_i^\nat/C_{i \bs i}^\nat$ cannot vary much when $E_i^\nat$ and 
$C_{i \bs i}^\nat$ are in the upper portions of their distributions.
In contrast, ``left'' histograms on the horizontal axis of D-F
can be highly variable, though only when $E_i$ and $C_{i \bs i}$
(or $E_i^\nat$ and $C_{i \bs i}^\nat$) are not tightly 
correlated in the left portions of their distributions.
The function pictured with a black line on panels D-F is simply the function
$z \rightarrow \ln(1-\delta+10^z)$ that takes $z=\log_{10}(E_1/C_{1 \bs 1})$
to $\ln(1-\delta+E_1/C_{1 \bs 1})$, the growth rate for the model.
Storage effects are manifest by this function, because it is flat on the left and 
upward sloping on the right, so highly variable horizontal-axis inputs to the function
can translate into higher average vertical-axis values than can concentrated
horizontal-axis inputs of the same mean; e.g., the histograms labeled ``left'' on
E,F. Vertical axis histograms on D-F are the results of applying the 
function represented by the black line on those panels to the corresponding
horizontal-axis histograms.
Red dots indicate the mean values of
each histogram. The average vertical-axis values of the two red dots on each panel
equal the GWR of species $i$ for the model (value displayed numerically,
labelled as ``growth'').

We now relate Fig. \ref{fig:beta_fecundidities_explanatory} back to ATA effects. Coexistence is possible for 
right-tail association (panel F, positive GWR) but impossible for left-tail association (panel D,
negative GWR). Coexistence is possible for the right-tail case essentially
because the points in the ``left'' region in C produce highly variable
annual growth rates, which lead to storage effects; the same effect does 
not occur for the left-tail case (panels A, D) because 
points in the ``left'' region on panel A are concentrated on line $L_1$ because of the
strong left-tail association of $E_i$ and $C_{i \bs i}$ on that panel. 
Association, or lack thereof, in right tails makes little difference 
to mean growth rates because $E_i/C_{i \bs i}$ cannot vary much. Overall, ATA effects 
are positive for the right-tail case because strong association between 
$E_i$ and $C_{i \bs i}$ is concentrated in the right tails, where there 
is little potential for storage effects anyway; and so disassociation between
$E_i$ and $C_{i \bs i}$ occurs in the left tails, where there is much potential for
storage effects. For the actual quantification of ATA effects,
a comparison is made to the case of symmetric association 
(panels B, E), as a benchmark. What is assessed by ATA
effects is the degree to which patterns of disassociation between 
$E$ and $C$ align with the portions of $E,C$ distribution for which the potential
for storage effects is high. Larger ATA effects come from better alignment.

Fig. \ref{fig:lognormal_fecundidities_explanatory} is similar to 
Fig. \ref{fig:beta_fecundidities_explanatory}, but is based on the log-normal 
fecundities lottery model instead of the beta fecundities lottery model. 
The figure illustrates that the potential for storage events is equivalent in
the upper and lower tails of the $EC$ distribution (labelled ``right'' and ``left'',
respectively, on panels A-C). That is why ATA effects are modest for the 
log-normal fecundities lottery model for the both the left- and right-tail
associated cases, and are negligible for the example parameters considered in 
Fig. \ref{fig:lognormal_fecundidities_explanatory}.

@@

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/PostHocExplanatoryFig_betaFecund.jpg}
\caption[A detailed look at ATA effects for the beta fecundities lottery model]{A 
detailed look at ATA effects for the beta fecundities lottery model.
The figure gives a pictorial representation of the calculation of  
$\E \left[ \ln \left( 1-\delta+\frac{E_i}{C_{i \bs i}} \right) \right]$ (A, C, D, F) and 
$\E \left[ \ln \left( 1-\delta+\frac{E_i^{||}}{C_{i \bs i}^{||}} \right) \right]$ (B, E)
for the model, considering both left- (A, D) and right-tail (C, F) associations
between $E_i$ and $C_{i \bs i}$. ATA effects are the first of these values minus the second.
The figure also illustrates how ATAs reflect the degree of alignment between where 
in the $EC$ distributions associations are allocated and which parts of that distribution
have high potential for storage effects. See SI section \ref{SIsect:intuition_examples}
for details. We used model parameters $\eta_1 = 1$, $\eta_2 = 1.2$, and $\delta=0.6$
for this example.}\label{fig:beta_fecundidities_explanatory}
\end{figure}
